\textbf{Preprinting Microbiology}

### 2017-02-13 submission/Schloss_PrePrints_mBio_2017.tex
Incorporate Stefano's edits

\textbf{\emph{Background.}} Many scientists, including microbiologists,
have begun to use preprints and other online venues such as social
media, blog posts, and videos as methods to garner attention for their
research and to engage the public. A preprint is an unpublished
manuscript that is made publicly available without going through an
official peer-review process (1--4). An author can post their manuscript
to a preprint server for others to read, share, and make comments.
Preprints were initially adopted among physicists and biologists in the
1960s as a method of sharing interesting research amongst colleagues
(5). While the biological community's commitment to preprints waned, the
physics community adopted what is now the \emph{arXiv} (pronounced
``archive'') preprint server that was hosted at the Los Alamos National
Laboratories from 1991 to 1999 and then at Cornell University (6). Among
physicists and mathematicians, posting a preprint to \emph{arXiv}
followed by submission to a peer-reviewed journal has become the
standard publication strategy. Although \emph{arXiv} has hosted a number
of computational biology papers, the server has not drawn widespread
attention from biologists. Among proponents of \emph{arXiv}, preprints
have aided in the development of research communication by accelerating
the release of the science and helping it to achieve a wider audience
for critique and reception (7). Considering the broadening adoption of
preprints among microbiologists, we sought to explore the specific uses
of and concerns regarding preprints.

\textbf{\emph{Landscape of preprint servers.}} In 2013, two preprint
servers, the \emph{bioRxiv} (pronounced ``bio-archive'') and \emph{PeerJ
Preprints}, were launched as preprint servers for biologists that would
parallel \emph{arXiv} (8). Both platforms offer similar features:
preprint posting is free; each preprint receives a digital object
identifier (DOI) that facilitates the ability to cite preprints in other
scholarly work; if the preprint is ever published, the preprint is
linked to the published version; the submission process for both options
is relatively simple allowing authors to upload a PDF version of their
preprint and supplemental materials; preprints are typically publicly
available in under 24 hours; they have built in venues for authors to
discuss their research with people who leave comments on the manuscript;
preprints undergo a basic screening process to remove submissions with
offensive or non-scientific content; and the sites provide article-level
metrics indicating the number of times an abstract has been accessed or
the preprint has been downloaded. There are several important
differences between the two options. First, \emph{PeerJ Prints} is a
for-profit organization and \emph{bioRxiv} is a non-profit organization
sponsored by Cold Spring Harbor Laboratory. This difference can be
meaningful to authors since some journals, including the American
Society for Microbiology (ASM) Journals, will only accept submissions
that have been posted on preprint servers hosted by non-profit
organizations. Second, preprints at \emph{PeerJ Preprints} are posted
under the Creative Commons Attribution License (CC-BY) and
\emph{bioRxiv} preprints can be posted under one of four CC-BY licenses
or with no permission for reuse. This can be relevant for authors hoping
to submit their work to a journal as journals will not consider
manuscripts posted as preprints under a CC-BY license (e.g.
\emph{Proceedings of the National Academy of Sciences}). A cosmetic, but
still relevant difference between the two is the layout and feel of the
two websites. Compared to the \emph{bioRxiv} site, the \emph{PeerJ
Preprint} site is more fluid, gives readers the ability to ``follow'' a
preprint, and provides better access to article keywords and the ability
to search preprints. With broader acceptance of preprints by traditional
journals, many journals, including all of the ASM journals, have
established mechanisms to directly submit manuscripts that are posted as
preprints on \emph{bioRxiv}. It is only possible to transfer a
\emph{PeerJ Preprint} for submission to \emph{PeerJ}. In many ways,
preprint servers have taken on the feel of a journal. As adoption of
this approach expands, it is likely that the features of these sites
will continue to improve. It is also likely that interfaces from
third-parties will improve. For example, although Google Scholar
includes preprints hosted at \emph{bioRxiv} and \emph{PeerJ Preprints}
in their search results, PubMed and Web of Science do not. There is also
hope that the National Institutes of Health (NIH) will renew their
interest in including preprints in PubMed search results. As preprint
servers begin to look and act like traditional journals by incorporating
features and interfaces, it will be important to balance the
requirements placed on authors for those features with the current
efficiency of the preprint format.

\textbf{\emph{Specific challenges for microbiology.}} Although preprints
offer an efficient and novel venue for disseminating microbiology
research, there are several considerations that the scientific community
and those that oversee preprint servers must consider. It is critical
that assurances be given that policies are in place to address these
issues. First, a significant amount of attention has been given to the
potential dual use of microbiology research for individuals seeking to
engage in terrorist activities. Second, for researchers engaging in
research that involves human subjects it is critical that assurances be
made that institutional review boards have been consulted and have
approved of the research. Third, there is significant concern regarding
researchers hiding potential conflicts of interest that could affect a
project's experimental design, analysis, and interpretation of results.
Finally, recent expansions in scientific publishing have revealed
numerous cases of plagiarism. Again, while hoping to maintain the
efficiency of the preprint format, traditional microbiology journals
have policies for these issues in place that should be easy to implement
by preprint servers.

\textbf{\emph{Acceptance of preprints by journals.}} An early
controversy encountered by researchers interested in posting their work
as preprints as a stage in disseminating their research was whether it
constituted prior publication. The broad consensus at this point is that
preprints do not constitute prior publication. This consensus is
reflected in the current policies of journals that commonly publish
microbiology research including those published by ASM, the Microbiology
Society, International Society for Microbial Ecology, PLOS, the
\emph{Proceedings of the National Academy of Science}, \emph{Science},
and \emph{Nature}, which have a permissive stance towards prior posting
of preprints prior to submission. Although journals published by Cell
Press do not forbid authors from posting preprints prior to submission,
they ask authors to consult an editor prior to posting and do not allow
authors to post revised preprints that contain revisions that respond to
editorial input. Considering the relatively fluid nature of many of
these policies and the journals' specific policies, prospective authors
should be aware of the positions taken by the journals where they may
eventually submit their work. Comprehensive lists of journals' attitudes
towards preprints are available online and are regularly updated (9,
10).

@@

\textbf{\emph{Preprints have the potential to change the advancement of
science.}} Preprints are often viewed as existing in a state of
scientific limbo. As noted above, they represent a formal communication,
but are not officially published. As the use of preprints grows and
scientists' perceptions of preprints matures, there are a number of
issues that will need to be addressed.

First, a common concern is that if a researcher posts their work as a
preprint, it will be ``scooped'' by another researcher and the preprint
author will lose their ability to claim primacy or their ability to
publish the work in a journal. Considering the preprint is a citable
work with a DOI, it would, in fact, be the preprint author that scooped
the second. A growing number of scientific societies and journals,
including ASM view preprints as citable and as having a legitimate claim
to primacy (1, 14--16). Some scientists worry that with such protection
a researcher can make a claim without valid data to support their claims
(3). This is possible; however, it is also the responsibility of the
scientific community to utilize the peer-review mechanisms that are
available to comment on those preprints pointing out methodological
problems or to indicate that they are speaking beyond the data.

A second area of concern is whether a preprint can be used to support a
grant proposal. Given the length limitations placed on grant proposals
by funding agencies, there is a push to cite previous work to indicate a
research team's competence in an area or to provide preliminary data.
Some fear that the use of preprints will allow scientists to circumvent
page limits by posting preliminary manuscripts. We would hope that both
consumers of preprints and grant proposal reviewers would be able to
differentiate between someone trying to game the system and someone that
is using preprints as a mechanism to improve their science.

@@

Beyond these concerns, preprints are also causing some to change their
publication goals. Some authors are explicitly stating that a preprint
will not be submitted to a journal (18). Although these authors may be a
minority of those who post preprints, such an approach may be attractive
to those that want to have a mechanism for people to cite a report of a
brief research communication, a critique of another publication, or
negative results. It is clear that the adoption of preprints will
challenge how scientists interact and evaluate each other's work. There
is great potential to empower researchers by controlling when a citable
piece of work is made public.

@@

Second, preprints have proven useful for rapidly correcting the
scientific literature. On February 9, 2015, \emph{Cell Systems} posted a
study by Afshinnekoo et al. online (19). The study collected and
analyzed metagenomic sequence data from the New York City subway system
and reported finding \emph{Yersinia pestis} and \emph{Bacillus
anthracis}. Because of the focus on these two bioterrorism agents, this
study generated a considerable amount of media attention. On April 25,
2015, Petit et al. (20) posted a preprint to Zenodo demonstrating that
there was no evidence for \emph{B. anthracis} in the dataset. On July
29, 2015, a critique was published by \emph{Cell Systems} along with a
response from the original authors offering a correction to their
manuscript (21, 22). A second anecdote of using preprints to aid in
post-publication peer-review surrounds the publishing of a draft
tardigrade genome in \emph{The Proceedings of the National Academy of
Sciences}. On November 23, 2015 a study by Boothby et al. (23) was first
published online. The authors posited that 17.5\% of its genes came from
bacteria, archaea, fungi, plants, and viruses. Another group had been
analyzing sequence data from a parallel tardigrade genome sequencing
project and did not observe the same result. A week later, on December
1, 2015, the second group had posted a preprint comparing the two genome
sequences and demonstrating that the exciting claims of horizontal gene
transfer were really the product of contaminants (24); this analysis
would eventually be published online by the original journal on March
24, 2016 followed by a rebuttal by the original authors on May 31, 2016
(25, 26). Two other analyses of the original data were published in May
2016 and a third was posted as a preprint on February 2, 2016 (27--29).
These anecdotes underscore the value of having a rapid posting cycle to
correcting errors in the scientific literature and that results posted
to preprint servers were able to correct the record within weeks of the
initial publication while the traditional path took six months in both
cases. A final notable case where preprints have accelerated the
correction of the scientific record was a preprint posted by Bik et al.
reporting numerous cases of image manipulation in peer reviewed studies
(30). Their preprint was posted on April 20, 2016 and published in
\emph{mBio} on June 7, 2016 (31). Instead of using preprints to react to
published papers that have been through peer review, it would be
interesting to consider how the editorial process for these examples and
the infamous ``Arsenic Life'' paper (32) would have been different had
they initially been posted as preprints.

@@

As stated above, preprints offer researchers the opportunity to improve
the quality of their work by adding a more formal and public step to the
scientific process. Among the microbiology-affiliated preprints, 146
(9.3\%) had been commented on at least once and only 35 (2.2\%) more
than three times using the \emph{bioRxiv}-hosted commenting feature.
Although the hosted commenting is only one mechanism for peer review,
this result was somewhat disturbing since the preprint model implicitly
depends on people's willingness to offer others feedback. Regardless,
authors do appear to be incorporating feedback from colleagues or
editorial insights from journals as 404 (25.8\%) of preprints were
revised at least once. Among the preprints posted prior to January 1,
2016, 31.6\% of the Microbiology category preprints, 35.1\% of the
microbiology-affiliated preprints, and 33.8\% of all preprints have been
published. As noted above, not all authors submit their preprints to
journals. This would indicate that the ``acceptance rates'' are actually
higher. Regardless, considering that these acceptance rates are higher
than many peer-reviewed journals (e.g.~approximately 20\% at ASM
Journals), these results dispel the critique that preprints represent
overly preliminary research.

Measuring the impact and significance of scientific research is
notoriously difficult. Using several metrics we sought to quantify the
effect that microbiology-affiliated preprints have had on the work of
others. Using the download statistics associated with each preprint, we
found that the median number of times an abstract or PDF had been
accessed was 923 (IQR: 603 to 1445) and 303 (IQR: 167 to 568),
respectively. These values represent two aspects of posting a preprint.
First, they reflect the number of times people were able to access
science before it was published. Second, they reflect the number of
times people were able to access a version of a manuscript that is
published behind a paywall. To obtain a measure of a preprint's ability
to garner attention and engage the public, we obtained the Altmetric
Attention Score for each preprint (\textbf{Figure 1B}). The Altmetric
Attention Score measures the number of times a preprint or paper is
mentioned in social media, traditional media, Wikipedia, policy
documents, and other sources (33). A higher score indicates that a
preprint received more attention. Microbiology-affiliated preprints have
had a median Altmetric Attention Score of 7.3 (IQR: 3.2 to 16.3) and
those of all preprints hosted at \emph{bioRxiv} have had a median score
of 7.0 (IQR: 3 to 15.6). For comparison, the median Altmetric Attention
Score for articles published in \emph{mBio} published since 2013 was 4.5
(IQR: 1.2 to 13.6). Of all scholarship tracked by Altmetric, the median
Altmetric Attention Score for preprints posted at \emph{biorxiv} ranks
at the 86 percentile (IQR: 66 to 94. A more traditional and
controversial metric of impact has been the number of citations an
article receives. We obtained the number of citations for the published
versions of manuscripts that were initially posted as preprints. To
allow for a comparison to traditional journals, we considered the
citations for preprints published in 2014 and 2015 as aggregated by Web
of Science (\textbf{Figure 1C}). Among the preprints that were published
and could be found in the Web of Science database, the median number of
citations was 6.5 (IQR: 2-14; mean: 13.6). For comparison, for the
papers published in \emph{mBio} in 2014 and 2015, the median number of
citations was 5 (IQR: 2-9; mean: 6.7). Although it is impossible to
quantify the quality or impact of research with individual metrics, it
is clear that preprints and the publications that result from them are
broadly accepted by the microbiology community

@@

\textbf{\emph{Preprints from a publisher's perspective.}} A lingering
question is what role traditional journals will have in disseminating
research if there is broad adoption of preprints. One perspective is
that although authors value immediate accessibility to their work, they
also value the editorial support from professional societies and other
organizations. Furthermore, the professional copyediting, layout, and
publicity that these publishers offer are also unique features of
traditional journals. An alternative perspective is that preprints will
eventually replace traditional journals. Certainly, this is a radical
perspective, but it does serve to motivate publishers to address what
they can offer preprint authors. By adopting preprint-friendly policies,
journals can create an attractive environment for authors. As discussed
above, a growing number of journals have created mechanisms for authors
to directly submit preprints to their journals. A new venture from
\emph{mSphere}, mSphereDirect, actively encourages authors to post their
manuscripts as preprints as part of the author-driven editorial process
(39). In addition to integrating preprints into the traditional
editorial process, several professional societies have also explicitly
supported citation of preprints in their other publications and
recognize the priority of preprints in the literature (14--16). These
are policies that empower authors and make specific journals more
attractive. Other practices have great potential to improve the
reputation of journals. As measured above, preprints are able to garner
attention on par with papers published in highly selective microbiology
journals. Thus, it is in a journal's best interest to recruit these
preprints to their journals. Several journals including \emph{PLOS
Genetics} and \emph{Genome Biology} have publicly stated that they scout
preprints for this purpose (40, 41). Preprints can also be viewed as a
lost opportunity to journals. A preprint that garners significant
attention may be ignored when it is finally published, brining little
additional attention to the journal. Going forward, it will be
interesting to see the innovative approaches that publishers develop so
that they can benefit by incorporating preprints into their process and
whether publishers' influence is reduced by the widespread adoption of
preprints.

@@

\textbf{Figure 1. Summary of microbiology-affiliated preprints since the
creation of} \textbf{\emph{biorxiv.}} The total number of preprints
posted for each quarter ending December 31, 2016 has largely tracked the
overall submission of preprints to \emph{biorxiv} (A). The Altmetric
attention scores of preprints posted to \emph{biorxiv} are similar to
those published in \emph{mBio} since November 2013 indicating preprints
engender a similar level of attention (B). The number of times preprints
that were published in 2014 and 2015 have been cited is similar to the
number of citations for papers published in \emph{mBio} in 2014 and 2015
indicates that published preprints are frequently cited (C). Regions
with common background shading in A are from the same year. The vertical
lines in B and C indicate the median Altmetric impact score and the
median number of citations.

>>>>

\textbf{\emph{Background.}} Many scientists, including microbiologists,
have begun to use preprints and other online venues such as social
media, blog posts, and videos as methods to garner attention for their
research and to engage the public. A preprint is an interim research
product, such as an unpublished manuscript, made publicly available
before going through an official peer-review process (1--4). Authors can
post their manuscript to a preprint server for others to read, share,
and comment. Preprints were initially adopted among physicists and
biologists in the 1960s as a method of sharing interesting research
amongst colleagues (5). While the biological community's commitment to
preprints waned, the physics community adopted what is now the
\emph{arXiv} (pronounced ``archive'') preprint server that was hosted at
the Los Alamos National Laboratories from 1991 to 1999 and then at
Cornell University (6). For some physicists and mathematicians, posting
a preprint to \emph{arXiv} followed by submission to a peer-reviewed
journal has become a standard publication pathway. Although \emph{arXiv}
has hosted a number of computational biology papers, the server has not
drawn widespread attention from biologists. Among proponents of
\emph{arXiv}, preprints have aided in the development of research
communication by accelerating the release of the science and helping it
to achieve a wider audience for critique and reception (7). Considering
the broadening adoption of preprints among microbiologists, we sought to
explore the specific uses of and concerns regarding preprints.

\textbf{\emph{Landscape of preprint servers.}} In 2013, two preprint
servers, the \emph{bioRxiv} (pronounced ``bio-archive'') and \emph{PeerJ
Preprints}, were launched as preprint servers for biologists that would
parallel \emph{arXiv} (8). Both platforms offer similar features:
preprint posting is free; each preprint receives a digital object
identifier (DOI) that facilitates the ability to cite preprints in other
scholarly work; if the preprint is ever published, the preprint is
linked to the published version; the submission process for both options
is relatively simple allowing authors to upload a PDF version of their
preprint and supplemental materials; preprints are typically publicly
available in about 24 hours; they have built in venues for authors to
discuss their research with people who leave comments on the manuscript;
preprints undergo a basic screening process to remove submissions with
offensive or non-scientific content; and the sites provide article-level
metrics indicating the number of times an abstract has been accessed or
the preprint has been downloaded. There are several important
differences between the two options. First, \emph{PeerJ Prints} is a
for-profit organization and \emph{bioRxiv} is a non-profit organization
sponsored by Cold Spring Harbor Laboratory. This difference can be
meaningful to authors since some journals, including the American
Society for Microbiology (ASM) Journals, will only accept submissions
that have been posted on preprint servers hosted by non-profit
organizations. Second, preprints at \emph{PeerJ Preprints} are posted
under the Creative Commons Attribution License (CC-BY) and
\emph{bioRxiv} preprints can be posted under one of four CC-BY licenses
or with no permission for reuse. This can be relevant for authors hoping
to submit their work to a journal as journals will not consider
manuscripts posted as preprints under a CC-BY license (e.g.
\emph{Proceedings of the National Academy of Sciences}). We particularly
like the \emph{bioRxiv} licensing flexibility, which empowers authors to
choose the model that best suits them, while ensuring the rapid posting
of their research resultsl however, it is important to provide clear
information to authors on the legal and practical tradeoffs of each
option. A cosmetic, but still relevant difference between the two is the
layout and feel of the two websites. Compared to the \emph{bioRxiv}
site, the \emph{PeerJ Preprint} site is more fluid, gives readers the
ability to ``follow'' a preprint, and provides better access to article
keywords and the ability to search preprints. With broader acceptance of
preprints by traditional journals, many journals, including all of the
ASM journals, have established mechanisms to directly submit manuscripts
that are posted as preprints on \emph{bioRxiv}. It is only possible to
transfer a \emph{PeerJ Preprint} for submission to \emph{PeerJ}. In many
ways, preprint servers have taken on the feel of a journal. As adoption
of this approach expands, it is likely that the features of these sites
will continue to improve. It is also likely that interfaces from
third-parties will improve. For example, although Google Scholar
includes preprints hosted at \emph{bioRxiv} and \emph{PeerJ Preprints}
in their search results, PubMed and Web of Science do not. There is also
hope that the National Institutes of Health (NIH) will renew their
interest in indexing preprints as separate research products than
peer-reviewed publications. As preprint servers begin to look and act
like traditional journals by incorporating features and interfaces, we
think that it is important to value the strength of the preprint - that
of an interim research product, nimble and quickly posted. It is
therefore essential to balance the requirements placed on authors for
features associated with preprints with the current desirable efficiency
of the preprint format.

\textbf{\emph{Specific challenges for microbiology.}} Although preprints
offer an efficient and novel venue for disseminating microbiology
research, there are several considerations that the scientific community
and those that oversee preprint servers must consider. It is critical
that assurances be given that policies are in place to address these
issues. First, a significant amount of attention has to be given to the
potential dual use research of concern (DURC) since posted results in
microbiology research could offer insights to individuals seeking to
engage in terrorist activities. Second, for researchers engaging in
research that involves human subjects it is critical that assurances be
made that institutional review boards have been consulted and have
approved of the research. Third, there is significant concern regarding
researchers hiding potential conflicts of interest that could affect a
project's experimental design, analysis, and interpretation of results.
Finally, recent expansions in scientific publishing have revealed
numerous cases of plagiarism or misconduct. Again, while hoping to
maintain the efficiency of the preprint format, traditional microbiology
journals have policies for these issues in place that should be easy to
implement by preprint servers.

\textbf{\emph{Acceptance of preprints by journals.}} An early
controversy encountered by researchers interested in posting their work
as preprints as a stage in disseminating their research was whether it
constituted prior publication. The broad consensus at this point is that
preprints do not constitute prior publication. This consensus is
reflected in the current policies of journals that commonly publish
microbiology research including those published by ASM, the Microbiology
Society, International Society for Microbial Ecology, PLOS, the
\emph{Proceedings of the National Academy of Science}, \emph{Science},
\emph{Nature} and Cell press, which each take a generally permissive
stance towards prior posting of preprints prior to submission.
Considering the relatively fluid nature of many of these policies and
the journals' specific policies, prospective authors should be aware of
the positions taken by the journals where they may eventually submit
their work. Comprehensive lists of journals' attitudes towards preprints
are available online and are regularly updated (9, 10).

@@

\textbf{\emph{Preprints have the potential to change the advancement of
science.}} Preprints are often viewed as existing in a state of
scientific limbo. As noted above, they represent a formal communication,
but an interim one, not officially published. As the use of preprints
grows and scientists' perceptions of preprints matures, there are a
number of issues that will need to be addressed.

First, a common concern is that if a researcher posts their work as a
preprint, it will be ``scooped'' by another researcher and the preprint
author will lose their ability to claim primacy or their ability to
publish the work in a journal. Considering the preprint is a citable
work with a DOI, it would, in fact, be the preprint author that scooped
the second. The use of preprints uncouples the communication of the
discovery from the relevance of the discovery, which will come later
based on peer-review, comments from other scientists at meetings or
online, and eventually citations. A growing number of scientific
societies and journals, including ASM view preprints as citable and as
having a legitimate claim to primacy (1, 14--16). Some scientists worry
that with such protection a researcher can make a claim without valid
data to support their claims (3). This is possible; however, it is also
the responsibility of the scientific community to utilize the
peer-review mechanisms that are available to comment on those preprints
pointing out methodological problems or to indicate that they are
speaking beyond the data.

A second area of concern is whether a preprint can be used to support a
grant proposal. Given the length limitations placed on grant proposals
by funding agencies, there is a push to cite previous work to indicate a
research team's competence in an area or to provide preliminary data.
Some fear that the use of preprints will allow scientists to circumvent
page limits by posting preliminary manuscripts. We would hope that both
consumers of preprints and grant proposal reviewers would be able to
differentiate between someone trying to game the system and someone that
is using preprints as a mechanism to improve their science. This would
be greatly facilitated if funding agencies would include preprints as
evidence for research progress, but listed separately from peer-reviewed
publications to help review panels in their decisions and to help author
substantiate evidence they feel they need to provide.

@@

Beyond these concerns, preprints are also causing some to change their
publication goals. Some authors are explicitly stating that a preprint
will not be submitted to a journal (18). Although these authors may be a
minority of those who post preprints, such an approach may be attractive
to those who need to cite a report of a brief research communication, a
critique of another publication, or negative results. It is clear that
the adoption of preprints will challenge how scientists interact and
evaluate each other's work. There is great potential to empower
researchers by controlling when a citable piece of work is made public.

@@

Second, preprints have proven useful for rapidly correcting the
scientific literature. On February 9, 2015, \emph{Cell Systems} posted a
study by Afshinnekoo et al. online (19). The study collected and
analyzed metagenomic sequence data from the New York City subway system
and reported finding \emph{Yersinia pestis} and \emph{Bacillus
anthracis}. Because of the focus on these two bioterrorism agents, this
study generated a considerable amount of media attention. On April 25,
2015, Petit et al. (20) posted a preprint to Zenodo demonstrating that
there was no evidence for \emph{B. anthracis} in the dataset. On July
29, 2015, a critique was published by \emph{Cell Systems} along with a
response from the original authors offering a correction to their
manuscript (21, 22). A second anecdote of using preprints to aid in
post-publication peer-review surrounds the publishing of a draft
tardigrade genome in \emph{The Proceedings of the National Academy of
Sciences}. On November 23, 2015 a study by Boothby et al. (23) was first
published online. The authors claimed that 17.5\% of its genes came from
bacteria, archaea, fungi, plants, and viruses. Another group had been
analyzing sequence data from a parallel tardigrade genome sequencing
project and did not observe the same result. A week later, on December
1, 2015, the second group had posted a preprint comparing the two genome
sequences and demonstrating that the exciting claims of horizontal gene
transfer were really the product of contaminants (24); this analysis
would eventually be published online by the original journal on March
24, 2016 followed by a rebuttal by the original authors on May 31, 2016
(25, 26). Two other analyses of the original data were published in May
2016 and a third was posted as a preprint on February 2, 2016 (27--29).
These anecdotes underscore the value of having a rapid posting cycle to
correcting errors in the scientific literature and that results posted
to preprint servers were able to correct the record within weeks of the
initial publication while the traditional path took six months in both
cases. A final notable case where preprints have accelerated the
correction of the scientific record was a preprint posted by Bik et al.
reporting numerous cases of image manipulation in peer reviewed studies
(30). Their preprint was posted on April 20, 2016 and published in
\emph{mBio} on June 7, 2016 (31). Instead of using preprints to react to
published papers that have been through peer review, it would be
interesting to consider how the editorial process for these examples and
the infamous ``Arsenic Life'' paper (32) would have been different had
they initially been posted as preprints.

@@

As stated above, preprints offer researchers the opportunity to improve
the quality of their work by adding a more formal and public step to the
scientific process. Among the microbiology-affiliated preprints, 146
(9.3\%) had been commented on at least once and only 35 (2.2\%) more
than three times using the \emph{bioRxiv}-hosted commenting feature.
Although the hosted commenting is only one mechanism for peer review,
this result was somewhat disturbing since the preprint model implicitly
depends on people's willingness to offer others feedback. We understand
that it is not in the tradition of the scientific community to comment
publicly online about colleagues' research results. We think this will
change given the possibilities of new media, and possibly incentives for
open commenting and reviewing could shift the trend. Importantly,
authors do appear to be incorporating feedback from colleagues or
editorial insights from journals as 404 (25.8\%) of preprints were
revised at least once. Among the preprints posted prior to January 1,
2016, 31.6\% of the Microbiology category preprints, 35.1\% of the
microbiology-affiliated preprints, and 33.8\% of all preprints have been
published. As noted above, not all authors submit their preprints to
journals. This would indicate that the ``acceptance rates'' are actually
higher. Regardless, considering that these acceptance rates are higher
than many peer-reviewed journals (e.g.~approximately 20\% at ASM
Journals), these results dispel the critique that preprints represent
overly preliminary research.

Measuring the impact and significance of scientific research is
notoriously difficult. Using several metrics we sought to quantify the
effect that broadly defined microbiology-affiliated preprints have had
on the work of others. Using the download statistics associated with
each preprint, we found that the median number of times an abstract or
PDF had been accessed was 923 (IQR: 603 to 1445) and 303 (IQR: 167 to
568), respectively. These values represent two aspects of posting a
preprint. First, they reflect the number of times people were able to
access science before it was published. Second, they reflect the number
of times people were able to access a version of a manuscript that is
published behind a paywall. To obtain a measure of a preprint's ability
to garner attention and engage the public, we obtained the Altmetric
Attention Score for each preprint (\textbf{Figure 1B}). The Altmetric
Attention Score measures the number of times a preprint or paper is
mentioned in social media, traditional media, Wikipedia, policy
documents, and other sources (33). A higher score indicates that a
preprint received more attention. Microbiology-affiliated preprints have
had a median Altmetric Attention Score of 7.3 (IQR: 3.2 to 16.3) and
those of all preprints hosted at \emph{bioRxiv} have had a median score
of 7.0 (IQR: 3 to 15.6). For comparison, the median Altmetric Attention
Score for articles published in \emph{mBio} published since 2013 was 4.5
(IQR: 1.2 to 13.6). Of all scholarship tracked by Altmetric, the median
Altmetric Attention Score for preprints posted at \emph{bioRxiv} ranks
at the 86 percentile (IQR: 66 to 94. A more traditional and
controversial metric of impact has been the number of citations an
article receives. We obtained the number of citations for the published
versions of manuscripts that were initially posted as preprints. To
allow for a comparison to traditional journals, we considered the
citations for preprints published in 2014 and 2015 as aggregated by Web
of Science (\textbf{Figure 1C}). Among the preprints that were published
and could be found in the Web of Science database, the median number of
citations was 6.5 (IQR: 2-14; mean: 13.6). For comparison, for the
papers published in \emph{mBio} in 2014 and 2015, the median number of
citations was 5 (IQR: 2-9; mean: 6.7). Although it is impossible to
quantify the quality or impact of research with individual metrics, it
is clear that preprints and the publications that result from them are
broadly accepted by the microbiology community.

@@

\textbf{\emph{Preprints from a publisher's perspective.}} A lingering
question is what role traditional journals will have in disseminating
research if there is broad adoption of preprints. We think that edited
peer-reviewed journals offer, and will continue to offer significant
added value to a publication. A scholarly publishing ecosystem in which
preprints coexist with journals will allow authors to gain value from
the immediate communication of their work associated with preprints and
also benefit from the peer-reviewed, professionally edited publication
that publishers can provide. The professional copyediting, layout, and
publicity that these publishers offer are also unique features of
traditional journals. An alternative perspective is that preprints will
eventually replace traditional journals. Certainly, this is a radical
perspective, but it does serve to motivate publishers to capture the
innovation opportunities offered by preprints. By adopting
preprint-friendly policies, journals can create an attractive
environment for authors. As discussed above, a growing number of
journals have created mechanisms for authors to directly submit
preprints to their journals. An example is offered by the ASM, which
earlier this year launched a new venture from \emph{mSphere}.
mSphereDirect is a publication track of the journal that capitalizes on
the opportunity offered to couple preprints with rigorous peer-review.
mSphereDirect. actively encourages authors to post their manuscripts as
preprints as part of an author-driven editorial process where an
editorial decision is rendered within five days and publication in
\emph{mSphere} within a month (39). ASM is developing a new platform,
MicroNow, which will help coalesce specific communities within the
microbial sciences, further enhancing the use of preprints as well as
published articles. In addition to integrating preprints into the
traditional editorial process, several professional societies have also
explicitly supported citation of preprints in their other publications
and recognize the priority of preprints in the literature (14--16).
These are policies that empower authors and make specific journals more
attractive. Other practices have great potential to improve the
reputation of journals. As measured above, preprints are able to garner
attention on par with papers published in highly selective microbiology
journals. Thus, it is in a journal's best interest to recruit these
preprints to their journals. Several journals including \emph{PLOS
Genetics} and \emph{Genome Biology} have publicly stated that they scout
preprints for this purpose (40, 41). Preprints can also be viewed as a
lost opportunity to journals. A preprint that garners significant
attention may be ignored when it is finally published, brining little
additional attention to the journal. Going forward, it will be
interesting to see the innovative approaches that publishers develop so
that they can benefit by incorporating preprints into their process and
whether publishers' influence is reduced by the widespread adoption of
preprints.

@@

\textbf{Figure 1. Summary of microbiology-affiliated preprints since the
creation of} \textbf{\emph{bioRxiv.}} The total number of preprints
posted for each quarter ending December 31, 2016 has largely tracked the
overall submission of preprints to \emph{bioRxiv} (A). The Altmetric
attention scores of preprints posted to \emph{bioRxiv} are similar to
those published in \emph{mBio} since November 2013 indicating preprints
engender a similar level of attention (B). The number of times preprints
that were published in 2014 and 2015 have been cited is similar to the
number of citations for papers published in \emph{mBio} in 2014 and 2015
indicates that published preprints are frequently cited (C). Regions
with common background shading in A are from the same year. The vertical
lines in B and C indicate the median Altmetric impact score and the
median number of citations.
